getdata3.Rmd

### 2021-12-18 getdata3.Rmd
continuing ...

Here we start with skum::pers instead of skum::obs, and age is always in days,
with stillbirth age 0.099 and born alive but dead on birthday at age 0.25 days.

Further, we skip the use of eha::make.communal in  favour of *match*. Reason: 
eha::make.communal assumes age is measured in *years*.

@@

>>>>

Here we start with *skum::pers* instead of *skum::obs*, and age is always in days,
with stillbirth age 0.099 and born alive but dead on birthday at age 0.25 days.

Further, we eventually skip the use of eha::make.communal in  favor of *match*. Reason: 
eha::make.communal assumes age is measured in *years*.

@@

Now we need *nofrs* for newborn, found in the *observation* file(s), so

```{r fromobs}
bobs <- obs[obs$starttyp == 2 & obs$id %in% per$id, ]

```
